Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-09 reports/manuscript/paper.tex
Remove author id from change markup. Add pyMergeChanges.py

\usepackage{changes}
% \definechangesauthor{name={Adam Richie-Halford}, color=red}{ARH}

@@

To assess the added value of incorporating anatomical knowledge into our
model, we compared our classification results to those obtained from
\replaced[id={ARH}]{four other models: a pure lasso model, an elastic net model, a
bundle-mean lasso (i.e. a lasso model trained only on the mean metric values
from each bundle), and a principal components regression lasso (Lasso PCR)
model \cite{powell2018local, rasero2021integrating}}{a lasso model}.
\replaced[id={ARH}]{These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\%
respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71,
respectively}{The pure lasso model achieved 76\% accuracy and an ROC AUC of
0.76} using the same cross-validation strategy used to assess the SGL model.
This difference in performance justifies the additional complexity of the SGL
over simpler sparsity-inducing regression strategies.

@@

As with ALS classification, we also compared SGL performance with results
obtained using \replaced[id={ARH}]{the pure lasso, elastic net, bundle-mean lasso, and
Lasso PCR}{only the lasso penalty}. The pure lasso models achieved $R^2 =
0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively
using the same cross-validation strategy used to assess the SGL. \added[id={ARH}]{The
elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN,
and Cam-CAN datasets, respectively. The bundle-mean lasso models achieved
$R^2 = 0.33$, $0.22$, and $0.55$, respectively. And the Lasso PCR models
achieved $R^2 = 0.54$, $0.57$, $0.74$, respectively.} The SGL models'
performance improvement over lasso is more modest than in the ALS
classification case, which accords with the selected values of the $\alpha$
hyperparameter. These SGL models were more lasso-like in their sparsity
penalties so they are more lasso-like in their predictive performance.

>>>>

\usepackage{changes}

@@

To assess the added value of incorporating anatomical knowledge into our
model, we compared our classification results to those obtained from
\replaced{four other models: a pure lasso model, an elastic net model, a
bundle-mean lasso (i.e. a lasso model trained only on the mean metric values
from each bundle), and a principal components regression lasso (Lasso PCR)
model \cite{powell2018local, rasero2021integrating}}{a lasso model}.
\replaced{These models achieved accuracies of 76\%, 76\%, 79.5\%, and 71.5\%
respectively and ROC AUC values of 0.76, 0.75, 0.82, and 0.71,
respectively}{The pure lasso model achieved 76\% accuracy and an ROC AUC of
0.76} using the same cross-validation strategy used to assess the SGL model.
This difference in performance justifies the additional complexity of the SGL
over simpler sparsity-inducing regression strategies.

@@

As with ALS classification, we also compared SGL performance with results
obtained using \replaced{the pure lasso, elastic net, bundle-mean lasso, and
Lasso PCR}{only the lasso penalty}. The pure lasso models achieved $R^2 =
0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively
using the same cross-validation strategy used to assess the SGL. \added{The
elastic net models achieved $R^2 = 0.46$, $0.59$, and $0.73$ for the WH, HBN,
and Cam-CAN datasets, respectively. The bundle-mean lasso models achieved
$R^2 = 0.33$, $0.22$, and $0.55$, respectively. And the Lasso PCR models
achieved $R^2 = 0.54$, $0.57$, $0.74$, respectively.} The SGL models'
performance improvement over lasso is more modest than in the ALS
classification case, which accords with the selected values of the $\alpha$
hyperparameter. These SGL models were more lasso-like in their sparsity
penalties so they are more lasso-like in their predictive performance.
